VM-Centric Snapshot Deduplication with Fault Isolation for Converged Cloud Architectures

### 2014-01-31 snapshot_system/paper.tex
fixed

\begin{document}

%\title{VM-Centric Deduplication with Fault Isolation for Virtual Machine Snapshot Backup }
%Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud}
\title{
VM-Centric  Snapshot Deduplication  with Fault Isolation 
for Converged Cloud Architectures} 
%VM-Centric  Deduplication  with Fault Isolation for Snapshot Backup in the Cloud
\author{
  Wei Zhang$^{\star}$, Michael Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  Hong Tang$^\dagger$\\
  {\normalsize$^\star$  University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.} \\
%  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com
}

@@

\begin{small}
\bibliographystyle{abbrv}
\bibliography{library,dedup1}
\end{small}
\end{document}

>>>>

%\linespread{.98} % to squeeeze lines and put figures in same page
\begin{document}

%\title{VM-Centric Deduplication with Fault Isolation for Virtual Machine Snapshot Backup }
%Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud}
\title{
VM-Centric  Snapshot Deduplication  with Fault Isolation 
for Converged Cloud Architectures} 
%VM-Centric  Deduplication  with Fault Isolation for Snapshot Backup in the Cloud
\author{
  Wei Zhang$^{\star}$, Daniel Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  Hong Tang$^\dagger$\\
  {\normalsize$^\star$University of California at Santa Barbara} \ \ {\normalsize$^\dagger$Alibaba Inc.} \\
%  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com
}

@@

\begin{small}
%\linespread{.97} % to squeeeze lines and put figures in same page
\bibliographystyle{abbrv}
\bibliography{library,dedup1}
\end{small}
\end{document}
